Programming Language Survey Paper on Haskell

### 2013-04-21 projects/term_paper/paper.tex
More updates. Got LaTeX Full working

Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and return values. Each functions acts independently of other functions, and does not change the state of anything outside of its scope. This is referred to as having no ``side-effects,'' and it allows Haskell to be exceptionally optimized and permit parallel processing. In addition, functions do not have to be declared in a particular order since they all exist independently of one another.

In addition, it is also a lazy language; expressions in Haskell are not evaluated at binding time, but rather are evaluated only when the result is needed.

@@

\subsection{Data Abstractions}
\subsubsection{Data Types}
Haskell includes many of the data types that are standard in most languages: Numbers, Characters, and Boolean values. Sub-data types for numbers exist to explicitly define characteristics of the type of number represented. For example, Haskell has two types of integers: Int and Integer. Int has the system-defined maximum integer size as its range while Integer’s ranged is only bound by the available amount of memory, and thus re used for arbitrary precision integers. Haskell also has two floating point types: Float and Double, where a Double has twice the floating point precision of a Float.

\begin{minted}{haskell}
let x = 2
let pi = 3.14
let c = 'c'
\end{minted}

@@

Haskell also has a String data type. Although Strings are represented by double quotations, they are actually stored as a list of characters. Thus, when specifiying a data type, String is equivalent to [Char].

\begin{minted}{haskell}
let str1 = ['H','a','s','k','e','l','l','!']
let str2 = "Haskell!" 	-- a string representation of str1
\end{minted}

>>>>

Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and return values. Every function acts independently of other functions and does not change the state of anything outside of its scope. This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as well as to permit parallel processing. In addition, functions do not have to be declared in a particular order since they all exist independently of one another.

@@

\subsection{Data Abstractions}
\subsubsection{Data Types}

Haskell includes many of the data types that are standard in most languages, such as Integers, Floats, Characters, and Boolean values.

\begin{minted}{haskell}
let x = 2
let pi = 3.14
let c = 'c'
let isHaskellAwesome = true
\end{minted}

@@

Haskell also allows the definition Strings, which are represented by surrounding text with double quotes. Strings, however, are not actually a data type. Although they can be initialized using the double quote syntax, the compiler converts the string into a list of characters at compile time. The use of the String notation is simply syntatic sugar for programmers. It also helps increase the readability of code. In the following example, the data is stored in the representation of str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in str2, which is much more understandable.

\begin{minted}{haskell}
let str1 = ['H','a','s','k','e','l','l','!']
let str2 = "Haskell!"
\end{minted}
